### 2020-10-27 manuscript/manuscript.rmd
small cleanups, animal_root -> animal_tree_root

#### Performance of data-recoding
All code used for the analyses presented here is available in a git repository at https://github.com/caseywdunn/animal_root/feuda_2017_response. The randomized recoding analyses are in the `recoding/alternative` subdirectory of the git repository.

>>>>

#### Performance of data-recoding
All code used for the analyses presented here is available in a git repository at https://github.com/caseywdunn/feuda_2017. The randomized recoding analyses are in the `recoding/alternative` subdirectory of the git repository.
